---
title: "Data_for_IS"
author: "Shivam K C"
date: "1/19/2021"
output: html_document
---
```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(car)
library(lme4)
library(lmerTest)
library(matlab)
library(gtools)
library(stringr)
library(purrr)
library(data.table)
library(writexl)
library(openxlsx)
library(neuralnet)
library(tidyr)
library(data.table)
```

```{r}
library("RSQLite")

## connect to db
con <- dbConnect(drv=RSQLite::SQLite(), dbname="database.sqlite")

## list all tables
tables <- dbListTables(con)

## exclude sqlite_sequence (contains table information)
tables <- tables[tables != "sqlite_sequence"]

lDataFrames <- vector("list", length=length(tables))

## create a data.frame for each table
for (i in seq(along=tables)) {
  lDataFrames[[i]] <- dbGetQuery(conn=con, statement=paste("SELECT * FROM '", tables[[i]], "'", sep=""))
  #lDataFrames <- map(tables, ~{
  #dbGetQuery(conn=con, statement=paste("SELECT * FROM '", .x, "'", sep=""))
#})
}
```

```{r}
lDataFrames[[3]]
```
#Getting Premier League Data for seasons 2008/2009 to 2015/2016
```{r}
premier_league <- lDataFrames[[3]] %>% filter(league_id == 1729)
```

#NArrowind down to 2009/2010 season
```{r}
premier_league_09_010 <- premier_league %>% filter(season == "2009/2010")
```

#Creating Goals_for varaible
```{r}
#First dividing in different stages

p_1 <- premier_league_09_010 %>% filter(stage == 1) # not predict the first gw of the season?
p_2 <- premier_league_09_010 %>% filter(stage == 2)

#p_2<- p_2 %>% mutate(home_team_goals_so_far = ifelse(home_team_api_id == p_1$home_team_api_id,p_1$home_team_goal,ifelse(home_team_api_id==p_1$away_team_api_id,p_1$away_team_goal, "NA")))

```

#Creating Goals_for variable [different approach]

```{r}
p_8650 <- premier_league_09_010 %>% filter(home_team_api_id == 	8650 | away_team_api_id == 	8650)

p_8650 <- p_8650 %>% mutate(TeamID = 8650)
p_8650 <- p_8650 %>% select(id, season, TeamID, stage, home_team_api_id,away_team_api_id, home_team_goal,away_team_goal,B365H,B365D,B365A)

p_8650 <- p_8650 %>% mutate(Goals_for = ifelse(TeamID==home_team_api_id,home_team_goal,away_team_goal))

p_8650 <- p_8650 %>% mutate(Goals_against = ifelse(TeamID==home_team_api_id,away_team_goal,home_team_goal))

#sorting by stage
p_8650 <- p_8650[order(p_8650$stage),]
#adding Goals_for_so_far

p_8650$Goals_for_so_far <- Reduce(function(u, v)  u + v , p_8650$Goals_for, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(Goals_for_so_far=lag(Goals_for_so_far)) #shifting the column down by one
```

#Creating Goals_against_so_far_in_season variable 
```{r}
#adding Goals_against_so_far

p_8650$Goals_against_so_far <- Reduce(function(u, v)  u + v , p_8650$Goals_against, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(Goals_against_so_far=lag(Goals_against_so_far)) #shifting the column down by one
```

#Creating overall_performance_so_far

```{r}
p_8650 <- p_8650 %>% mutate(scoreline_difference_h_a = home_team_goal - away_team_goal)
p_8650 <- p_8650 %>% mutate(record = ifelse(TeamID==home_team_api_id & scoreline_difference_h_a > 0, "W",ifelse(TeamID==home_team_api_id & scoreline_difference_h_a < 0, "L",ifelse(TeamID==home_team_api_id & scoreline_difference_h_a ==0, "D",ifelse(TeamID==away_team_api_id & scoreline_difference_h_a > 0, "L",ifelse(TeamID==away_team_api_id & scoreline_difference_h_a < 0,"W","D")))))) #win loss draw

#points distribution

p_8650 <- p_8650 %>% mutate(point = ifelse(record=="W",3,ifelse(record=="L",0,1)))

#Gotta do recursive accumulation for the overall performacne so far

p_8650$overall_performance_so_far <- Reduce(function(u, v)  u + v , p_8650$point, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(overall_performance_so_far=lag(overall_performance_so_far)) #shifting the column down by one
```

#Creating cumulative home performance and away performance

```{r}
p_8650 <- p_8650 %>% mutate(home_performance_point = ifelse(TeamID==home_team_api_id,point,0) )

#Gotta do recursive accumulation for cumulative home performance so far

p_8650$cum_home_performance_so_far <- Reduce(function(u, v)  u + v , p_8650$home_performance_point, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(cum_home_performance_so_far=lag(cum_home_performance_so_far)) #shifting the column down by one


p_8650 <- p_8650 %>% mutate(away_performance_point = ifelse(TeamID==away_team_api_id,point,0) )

#Gotta do recursive accumulation for cumulative home performance so far

p_8650$cum_away_performance_so_far <- Reduce(function(u, v)  u + v , p_8650$away_performance_point, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(cum_away_performance_so_far=lag(cum_away_performance_so_far)) #shifting the column down by one
```

#Creating performance in previous game

```{r}
p_8650<-p_8650 %>% mutate(performance_in_previous_game=lag(point))
```

#Creating Location variable

```{r}
p_8650<-p_8650 %>% mutate(location= ifelse(TeamID==home_team_api_id,1,0))
```

#Creating average performance in previous n games

```{r}
#p_8650<-p_8650 %>% mutate(performance_in_previous_2_games= ifelse(TeamID==home_team_api_id,1,0))

#DT[ , D := C + shift(B, 1L, type="lag")]
p_8650<-as.data.table(p_8650)
p_8650$performance_in_previous_2_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag"))/2  #performance_in_previous_2_games

#performance_in_previous_3_games
p_8650$performance_in_previous_3_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag")+shift(p_8650$point, 3, type="lag"))/3  

#performance_in_previous_4_games
p_8650$performance_in_previous_4_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag")+shift(p_8650$point, 3, type="lag")+shift(p_8650$point, 4, type="lag"))/4  

#performance_in_previous_5_games
p_8650$performance_in_previous_5_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag")+shift(p_8650$point, 3, type="lag")+shift(p_8650$point, 4, type="lag")+shift(p_8650$point, 5, type="lag"))/5  

#performance_in_previous_6_games
p_8650$performance_in_previous_6_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag")+shift(p_8650$point, 3, type="lag")+shift(p_8650$point, 4, type="lag")+shift(p_8650$point, 5, type="lag")+shift(p_8650$point, 6, type="lag"))/6  
```

#Creating goals-for in previous n games

```{r}
#goals_for_in_previous_1_game
p_8650$goals_for_in_previous_1_game<- shift(p_8650$Goals_for, 1, type="lag")

#goals_for_in_previous_2_games
p_8650$goals_for_in_previous_2_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag"))/2

#goals_for_in_previous_3_games
p_8650$goals_for_in_previous_3_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag")+shift(p_8650$Goals_for, 3, type="lag"))/3

#goals_for_in_previous_4_games
p_8650$goals_for_in_previous_4_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag")+shift(p_8650$Goals_for, 3, type="lag")+shift(p_8650$Goals_for, 4, type="lag"))/4

#goals_for_in_previous_5_games
p_8650$goals_for_in_previous_5_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag")+shift(p_8650$Goals_for, 3, type="lag")+shift(p_8650$Goals_for, 4, type="lag")+shift(p_8650$Goals_for, 5, type="lag"))/5

#goals_for_in_previous_6_games
p_8650$goals_for_in_previous_6_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag")+shift(p_8650$Goals_for, 3, type="lag")+shift(p_8650$Goals_for, 4, type="lag")+shift(p_8650$Goals_for, 5, type="lag")+shift(p_8650$Goals_for, 6, type="lag"))/6
```

#Creating goals-against in previous n games

```{r}
#goals_against_in_previous_1_game
p_8650$goals_against_in_previous_1_game<- shift(p_8650$Goals_against, 1, type="lag")

#goals_against_in_previous_2_games
p_8650$goals_against_in_previous_2_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag"))/2

#goals_against_in_previous_3_games
p_8650$goals_against_in_previous_3_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag")+shift(p_8650$Goals_against, 3, type="lag"))/3

#goals_against_in_previous_4_games
p_8650$goals_against_in_previous_4_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag")+shift(p_8650$Goals_against, 3, type="lag")+shift(p_8650$Goals_against, 4, type="lag"))/4

#goals_against_in_previous_5_games
p_8650$goals_against_in_previous_5_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag")+shift(p_8650$Goals_against, 3, type="lag")+shift(p_8650$Goals_against, 4, type="lag")+shift(p_8650$Goals_against, 5, type="lag"))/5

#goals_against_in_previous_6_games
p_8650$goals_against_in_previous_6_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag")+shift(p_8650$Goals_against, 3, type="lag")+shift(p_8650$Goals_against, 4, type="lag")+shift(p_8650$Goals_against, 5, type="lag")+shift(p_8650$Goals_against, 6, type="lag"))/6
```

#Writing the file to excel

```{r}

p_8650 <-as.data.frame(p_8650)
write_xlsx(p_8650, 'premier_league_2009_10_p_8650')
```

#Cleaning data for 20 teams for 2009/2010 season

```{r}
#Let's use for loop

y <- unique(premier_league$season)
combineddataset <-data.table() #creating empty data.table () to later append!!!
for (j in y){
  premier_league_09_010 <- premier_league %>% filter(season == j) #NArrowind down to particular season
  x <-  unique(premier_league_09_010$home_team_api_id)
for (i in x){
#First let's try a different team 10260

#Creating Goals_for variable [different approach]

p_8650 <- premier_league_09_010 %>% filter(home_team_api_id == 	i | away_team_api_id == 	i)

p_8650 <- p_8650 %>% mutate(TeamID = i)
p_8650 <- p_8650 %>% select(id, season, TeamID, stage, home_team_api_id,away_team_api_id, home_team_goal,away_team_goal,B365H,B365D,B365A)

p_8650 <- p_8650 %>% mutate(Goals_for = ifelse(TeamID==home_team_api_id,home_team_goal,away_team_goal))

p_8650 <- p_8650 %>% mutate(Goals_against = ifelse(TeamID==home_team_api_id,away_team_goal,home_team_goal))

#sorting by stage
p_8650 <- p_8650[order(p_8650$stage),]
#adding Goals_for_so_far

p_8650$Goals_for_so_far <- Reduce(function(u, v)  u + v , p_8650$Goals_for, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(Goals_for_so_far=lag(Goals_for_so_far)) #shifting the column down by one


#Creating Goals_against_so_far_in_season variable 

#adding Goals_against_so_far

p_8650$Goals_against_so_far <- Reduce(function(u, v)  u + v , p_8650$Goals_against, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(Goals_against_so_far=lag(Goals_against_so_far)) #shifting the column down by one


#Creating overall_performance_so_far


p_8650 <- p_8650 %>% mutate(scoreline_difference_h_a = home_team_goal - away_team_goal)
p_8650 <- p_8650 %>% mutate(record = ifelse(TeamID==home_team_api_id & scoreline_difference_h_a > 0, "W",ifelse(TeamID==home_team_api_id & scoreline_difference_h_a < 0, "L",ifelse(TeamID==home_team_api_id & scoreline_difference_h_a ==0, "D",ifelse(TeamID==away_team_api_id & scoreline_difference_h_a > 0, "L",ifelse(TeamID==away_team_api_id & scoreline_difference_h_a < 0,"W","D")))))) #win loss draw

#points distribution

p_8650 <- p_8650 %>% mutate(point = ifelse(record=="W",3,ifelse(record=="L",0,1)))

#Gotta do recursive accumulation for the overall performacne so far

p_8650$overall_performance_so_far <- Reduce(function(u, v)  u + v , p_8650$point, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(overall_performance_so_far=lag(overall_performance_so_far)) #shifting the column down by one


#Creating cumulative home performance and away performance


p_8650 <- p_8650 %>% mutate(home_performance_point = ifelse(TeamID==home_team_api_id,point,0) )

#Gotta do recursive accumulation for cumulative home performance so far

p_8650$cum_home_performance_so_far <- Reduce(function(u, v)  u + v , p_8650$home_performance_point, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(cum_home_performance_so_far=lag(cum_home_performance_so_far)) #shifting the column down by one


p_8650 <- p_8650 %>% mutate(away_performance_point = ifelse(TeamID==away_team_api_id,point,0) )

#Gotta do recursive accumulation for cumulative home performance so far

p_8650$cum_away_performance_so_far <- Reduce(function(u, v)  u + v , p_8650$away_performance_point, init = 0, accumulate = TRUE)[-1]


p_8650<-p_8650 %>% mutate(cum_away_performance_so_far=lag(cum_away_performance_so_far)) #shifting the column down by one


#Creating performance in previous game


p_8650<-p_8650 %>% mutate(performance_in_previous_game=lag(point))


#Creating Location variable


p_8650<-p_8650 %>% mutate(location= ifelse(TeamID==home_team_api_id,1,0))


#Creating average performance in previous n games




#DT[ , D := C + shift(B, 1L, type="lag")]
p_8650<-as.data.table(p_8650)
p_8650$performance_in_previous_2_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag"))/2  #performance_in_previous_2_games

#performance_in_previous_3_games
p_8650$performance_in_previous_3_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag")+shift(p_8650$point, 3, type="lag"))/3  

#performance_in_previous_4_games
p_8650$performance_in_previous_4_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag")+shift(p_8650$point, 3, type="lag")+shift(p_8650$point, 4, type="lag"))/4  

#performance_in_previous_5_games
p_8650$performance_in_previous_5_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag")+shift(p_8650$point, 3, type="lag")+shift(p_8650$point, 4, type="lag")+shift(p_8650$point, 5, type="lag"))/5  

#performance_in_previous_6_games
p_8650$performance_in_previous_6_games<- (shift(p_8650$point, 1, type="lag") + shift(p_8650$point, 2, type="lag")+shift(p_8650$point, 3, type="lag")+shift(p_8650$point, 4, type="lag")+shift(p_8650$point, 5, type="lag")+shift(p_8650$point, 6, type="lag"))/6  


#Creating goals-for in previous n games


#goals_for_in_previous_1_game
p_8650$goals_for_in_previous_1_game<- shift(p_8650$Goals_for, 1, type="lag")

#goals_for_in_previous_2_games
p_8650$goals_for_in_previous_2_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag"))/2

#goals_for_in_previous_3_games
p_8650$goals_for_in_previous_3_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag")+shift(p_8650$Goals_for, 3, type="lag"))/3

#goals_for_in_previous_4_games
p_8650$goals_for_in_previous_4_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag")+shift(p_8650$Goals_for, 3, type="lag")+shift(p_8650$Goals_for, 4, type="lag"))/4

#goals_for_in_previous_5_games
p_8650$goals_for_in_previous_5_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag")+shift(p_8650$Goals_for, 3, type="lag")+shift(p_8650$Goals_for, 4, type="lag")+shift(p_8650$Goals_for, 5, type="lag"))/5

#goals_for_in_previous_6_games
p_8650$goals_for_in_previous_6_games<- (shift(p_8650$Goals_for, 1, type="lag")+shift(p_8650$Goals_for, 2, type="lag")+shift(p_8650$Goals_for, 3, type="lag")+shift(p_8650$Goals_for, 4, type="lag")+shift(p_8650$Goals_for, 5, type="lag")+shift(p_8650$Goals_for, 6, type="lag"))/6

#Creating goals-against in previous n games

#goals_against_in_previous_1_game
p_8650$goals_against_in_previous_1_game<- shift(p_8650$Goals_against, 1, type="lag")

#goals_against_in_previous_2_games
p_8650$goals_against_in_previous_2_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag"))/2

#goals_against_in_previous_3_games
p_8650$goals_against_in_previous_3_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag")+shift(p_8650$Goals_against, 3, type="lag"))/3

#goals_against_in_previous_4_games
p_8650$goals_against_in_previous_4_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag")+shift(p_8650$Goals_against, 3, type="lag")+shift(p_8650$Goals_against, 4, type="lag"))/4

#goals_against_in_previous_5_games
p_8650$goals_against_in_previous_5_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag")+shift(p_8650$Goals_against, 3, type="lag")+shift(p_8650$Goals_against, 4, type="lag")+shift(p_8650$Goals_against, 5, type="lag"))/5

#goals_against_in_previous_6_games
p_8650$goals_against_in_previous_6_games<- (shift(p_8650$Goals_against, 1, type="lag")+shift(p_8650$Goals_against, 2, type="lag")+shift(p_8650$Goals_against, 3, type="lag")+shift(p_8650$Goals_against, 4, type="lag")+shift(p_8650$Goals_against, 5, type="lag")+shift(p_8650$Goals_against, 6, type="lag"))/6

#append the files here:

combineddataset = rbind(combineddataset,p_8650)
}
#Writing the file to excel
combineddataset <-as.data.frame(combineddataset)
write_xlsx(combineddataset, 'premier_league_8_seasons_cleaned')
}
```


#Running ANN

```{r}
#Get the data and as factor W,L,D in an ordered fashion

cd <- combineddataset #let cd be a normalized dataset!
#cd$outcome <- factor(cd$record, ordered = TRUE, levels=c("L","D","W")) (i)
cd <- cd %>% mutate(outcome = ifelse(record=="W",1,ifelse(record=="L",0,ifelse(record=="D",0.5,"NA")))) #I wonder (i) is better than this for ANN output unit?

# before normalizign , take care of NAs and categorical variables
cd <- cd %>% select(-performance_in_previous_6_games,-goals_for_in_previous_6_games,-goals_against_in_previous_6_games) #change here if you want to include last 6 games performance

cd <- cd %>% select(-record)

cd<-na.omit(cd)

#Normalizing data before speparation of trai nand test and doing  ANN

cd$outcome <- as.numeric(cd$outcome) # this mkaes difference in output unit of ANN
for (i in 8: (ncol(cd))-1){ #careful with this line of code
  cd[,i] <- (cd[,i]-min(cd[,i]))/(max(cd[,i])-min(cd[,i]))
}

```



```{r}
# First separate train and test data
train_data <- cd %>% filter(season == "2008/2009" 
                            |season == "2009/2010"|season == "2010/2011"|season == "2011/2012"|season == "2012/2013"|season == "2013/2014"
                            )
#%>% select(-performance_in_previous_6_games,-goals_for_in_previous_6_games,-goals_against_in_previous_6_games) [MIGHT NEED THIS LATER WHEN USING LAST 6 GWS!]

test_data <- cd %>% filter(season == "2014/2015" |season == "2015/2016")
#%>% select(-performance_in_previous_6_games,-goals_for_in_previous_6_games,-goals_against_in_previous_6_games)
# Taking care of NA's

#Removing NA's from train and test data initially;
train_data<-na.omit(train_data) #only do na.omit for until first 5 gws initially!
test_data<-na.omit(test_data)
```

#Let's experiment with reshuffling and then dividing the train and test data
```{r}
#set.seed(1234)
#train_data<-train_data[sample(nrow(train_data)),] #didn't work!
```

#Be careful when rerunning the following ANN code; it will change as weights change!

```{r}
# Using neuralnet on train data, get the confidence levels for each teams in a match
# probably want to set.seed(1234)?
set.seed(1236)
#nn = neuralnet(outcome~
                 #Goals_for_so_far+Goals_against_so_far+
                 #cum_home_performance_so_far+cum_away_performance_so_far
               #+performance_in_previous_game+performance_in_previous_2_games+
                # performance_in_previous_3_games
               #+performance_in_previous_4_games
               #+performance_in_previous_5_games+goals_for_in_previous_2_games+goals_for_in_previous_1_game+goals_for_in_previous_3_games+goals_for_in_previous_4_games+goals_for_in_previous_5_games+location+goals_against_in_previous_1_game+goals_against_in_previous_2_games+goals_against_in_previous_3_games+goals_against_in_previous_4_games+goals_against_in_previous_5_games
            #   , data=train_data,hidden = c(1), algorithm = "backprop",err.fct = "sse",linear.output =FALSE,learningrate = 0.05) #change to 0.03 and 10,10,10 #graphs of different leraning rates vs steps / errors; graphs of different thresholds are good idea for more research!
#Later, check what happens when the following is done:
  #likelihood = true OR
  #when 6 gws are taken into account
  #different act.fct is used
  #different err.fct is used
  #different learning rate is used
#21 variables
```

#Let's experiment with different nnet package
```{r}
set.seed(1235)
library(nnet)
nnet_mod <- nnet(outcome~
                 Goals_for_so_far+Goals_against_so_far+
                 cum_home_performance_so_far+cum_away_performance_so_far
               +performance_in_previous_game+performance_in_previous_2_games+
                 performance_in_previous_3_games
               +performance_in_previous_4_games
               +performance_in_previous_5_games+goals_for_in_previous_2_games+goals_for_in_previous_1_game+goals_for_in_previous_3_games+goals_for_in_previous_4_games+goals_for_in_previous_5_games+location+goals_against_in_previous_1_game+goals_against_in_previous_2_games+goals_against_in_previous_3_games+goals_against_in_previous_4_games+goals_against_in_previous_5_games,
               data=train_data, size = 10,  maxit=10, trace=T)
```
#Let's see the putut of nnet model!
```{r}
v<-nnet_mod$fitted.values
#View(v)
```
#Let's predict using ANN1
```{r}
#changing name of the output from nnet to confidence_score_of a team!
confidence_score<-v
#combining nnoutput_scaled to the train dataset 
nnet_train_combined <- cbind(train_data,confidence_score)

#Just checking
#covariate<-nn$covariate
```
#Calculating Home team confidence score - ATCS for each game Then making predictions using different thresholds!
```{r}

# Befoew pivoting, let's get Actual outcome in the form of H/A/D

nnet_train_combined <- nnet_train_combined %>% mutate(Actual_outcome = ifelse(outcome==0.5,"D",ifelse((outcome==1 & TeamID==home_team_api_id)|(outcome==0 & TeamID == away_team_api_id),"H","A")))


```
#Pivoting for nnet train dataset
```{r}
#Pivot the dataset [might have to do it for test dataset later on] such that you have only one row for each game: Also, you have a column of either Home Win/ Away Win/ Draw [Actual Outcome]

# Pivot dataset? so that each match id have only one row? it will be 1980 training matches



pivot_nnet_train_combined <-dcast(setDT(nnet_train_combined), id~rowid(id), value.var=c("TeamID", "home_team_api_id","away_team_api_id","confidence_score","Actual_outcome"))


#Gettig home confidence score and ACS:
pivot_nnet_train_combined <- pivot_nnet_train_combined %>% mutate(HCS = ifelse(home_team_api_id_1==TeamID_1,confidence_score_1,ifelse(home_team_api_id_1==TeamID_2,confidence_score_2,"NA")))

pivot_nnet_train_combined$HCS <- as.numeric(pivot_nnet_train_combined$HCS)

pivot_nnet_train_combined <- pivot_nnet_train_combined %>% mutate(ACS = ifelse(away_team_api_id_1==TeamID_1,confidence_score_1,ifelse(away_team_api_id_1==TeamID_2,confidence_score_2,"NA"))) 

pivot_nnet_train_combined$ACS <- as.numeric(pivot_nnet_train_combined$ACS)

#Calculate HT_CL - AwayTeam_ConfidenceLevel

pivot_nnet_train_combined <- pivot_nnet_train_combined %>% mutate(difference_in_CS_H = HCS - ACS)

#Add the HTCL - ATCL score such that you can create column of Predicted_Outcome

#then create confusion matrix using Predicted_Outcome vs Actual Outcome
```
# NNET predictions for train data for ANN1
```{r}
#creating thresholds for predicted Home winning/A/D

pivot_nnet_train_combined <- pivot_nnet_train_combined %>% mutate(Predicted_outcome = ifelse(abs(difference_in_CS_H) == 0,"D",ifelse(difference_in_CS_H>0,"H",ifelse(difference_in_CS_H<0,"A","NA"))))
```

```{r}
#With the above threshold, get confusion matrix:
attach(pivot_nnet_train_combined)
table(Actual_outcome_1,Predicted_outcome)

#if thresholds are: 0 for D, >0 for H, and < 0 for A, then accuracy = 58.6 % [I WONDER HOW MUCH PROFIT WOULD I MAKE FROM THIS SUCCESS RATE, PREDICTING MOSTLY AWAY WINS!]
```
#Let's predict nnet (ANN1) on test data

```{r}

nnet_p <- predict(object = nnet_mod,newdata= test_data,type="raw") #why?
```
# I need to pivot the test data as well
```{r}
#changing name of the output from nnet to confidence_score_of a team!
confidence_score<-nnet_p
#combining nnoutput_scaled to the train dataset 
nnet_test_combined <- cbind(test_data,confidence_score)

#Just checking
#covariate<-nn$covariate
```
#Calculating Home team confidence score - ATCS for each game Then making predictions using different thresholds!
```{r}

# Befoew pivoting, let's get Actual outcome in the form of H/A/D

nnet_test_combined <- nnet_test_combined %>% mutate(Actual_outcome = ifelse(outcome==0.5,"D",ifelse((outcome==1 & TeamID==home_team_api_id)|(outcome==0 & TeamID == away_team_api_id),"H","A")))


```
#Pivoting for nnet train dataset
```{r}
#Pivot the dataset [might have to do it for test dataset later on] such that you have only one row for each game: Also, you have a column of either Home Win/ Away Win/ Draw [Actual Outcome]

# Pivot dataset? so that each match id have only one row? it will be 1980 training matches



pivot_nnet_test_combined <-dcast(setDT(nnet_test_combined), id~rowid(id), value.var=c("TeamID", "home_team_api_id","away_team_api_id","confidence_score","Actual_outcome"))


#Gettig home confidence score and ACS:
pivot_nnet_test_combined <- pivot_nnet_test_combined %>% mutate(HCS = ifelse(home_team_api_id_1==TeamID_1,confidence_score_1,ifelse(home_team_api_id_1==TeamID_2,confidence_score_2,"NA")))

pivot_nnet_test_combined$HCS <- as.numeric(pivot_nnet_test_combined$HCS)

pivot_nnet_test_combined <- pivot_nnet_test_combined %>% mutate(ACS = ifelse(away_team_api_id_1==TeamID_1,confidence_score_1,ifelse(away_team_api_id_1==TeamID_2,confidence_score_2,"NA"))) 

pivot_nnet_test_combined$ACS <- as.numeric(pivot_nnet_test_combined$ACS)

#Calculate HT_CL - AwayTeam_ConfidenceLevel

pivot_nnet_test_combined <- pivot_nnet_test_combined %>% mutate(difference_in_CS_H = HCS - ACS)

#Add the HTCL - ATCL score such that you can create column of Predicted_Outcome

#then create confusion matrix using Predicted_Outcome vs Actual Outcome
```
# NNET predictions for test data for ANN1
```{r}
#creating thresholds for predicted Home winning/A/D

pivot_nnet_test_combined <- pivot_nnet_test_combined %>% mutate(Predicted_outcome = ifelse(abs(difference_in_CS_H) == 0,"D",ifelse(difference_in_CS_H>0,"H",ifelse(difference_in_CS_H<0,"A","NA"))))
```

```{r}
#With the above threshold, get confusion matrix:
attach(pivot_nnet_test_combined)
table(Actual_outcome_1,Predicted_outcome)

#if thresholds are: 0 for D, >0 for H, and < 0 for A, then accuracy = 44.2 % [I WONDER HOW MUCH PROFIT WOULD I MAKE FROM THIS SUCCESS RATE, PREDICTING MOSTLY AWAY WINS!]

#since the predictive accuracy for test data is low, probably problem of overfitting! Shall I do treshold? and then do crossvalidation?

# it seems like if i decreased iteration in train, the PA for train decreases but for test, it increases
```
#This is neural net's stuffs
```{r}
# checking nn from neural net
#nn
#plot(nn)
#a<-nn$net.result[[1]]
#View(a)
#garson(nn)

```

```{r}
#result_nn_matrix <- nn$result.matrix #to summarize results from the model
```

```{r}
#Getting the predicted values from 
#a<-nn$net.result[[1]]

#Scaling the output values from neural network between 0 and 1!
#nn_output_scaled <- a
#nn_output_scaled[,1] <- (nn_output_scaled[,1]-min(nn_output_scaled[,1]))/(max(nn_output_scaled[,1])-min(nn_output_scaled[,1])) #normalized between 0 and 1!

#actual_output <- train_data$outcome
```

```{r}
#changing name of the output from NN to confidence_score_of a team!
confidence_score<-nn_output_scaled
#combining nnoutput_scaled to the train dataset 
nn_train_combined <- cbind(train_data,confidence_score)

#Just checking
#covariate<-nn$covariate
```

#Calculating Home team confidence score - ATCS for each game Then making predictions using different thresholds!
```{r}

# Befoew pivoting, let's get Actual outcome in the form of H/A/D

nn_train_combined <- nn_train_combined %>% mutate(Actual_outcome = ifelse(outcome==0.5,"D",ifelse((outcome==1 & TeamID==home_team_api_id)|(outcome==0 & TeamID == away_team_api_id),"H","A")))


```

```{r}
#Pivot the dataset [might have to do it for test dataset later on] such that you have only one row for each game: Also, you have a column of either Home Win/ Away Win/ Draw [Actual Outcome]

# Pivot dataset? so that each match id have only one row? it will be 1980 training matches



pivot_nn_train_combined <-dcast(setDT(nn_train_combined), id~rowid(id), value.var=c("TeamID", "home_team_api_id","away_team_api_id","confidence_score","Actual_outcome"))


#Gettig home confidence score and ACS:
pivot_nn_train_combined <- pivot_nn_train_combined %>% mutate(HCS = ifelse(home_team_api_id_1==TeamID_1,confidence_score_1,ifelse(home_team_api_id_1==TeamID_2,confidence_score_2,"NA")))

pivot_nn_train_combined$HCS <- as.numeric(pivot_nn_train_combined$HCS)

pivot_nn_train_combined <- pivot_nn_train_combined %>% mutate(ACS = ifelse(away_team_api_id_1==TeamID_1,confidence_score_1,ifelse(away_team_api_id_1==TeamID_2,confidence_score_2,"NA"))) 

pivot_nn_train_combined$ACS <- as.numeric(pivot_nn_train_combined$ACS)

#Calculate HT_CL - AwayTeam_ConfidenceLevel

pivot_nn_train_combined <- pivot_nn_train_combined %>% mutate(difference_in_CS_H = HCS - ACS)

#Add the HTCL - ATCL score such that you can create column of Predicted_Outcome

#then create confusion matrix using Predicted_Outcome vs Actual Outcome
```

```{r}
#creating thresholds for predicted Home winning/A/D

pivot_nn_train_combined <- pivot_nn_train_combined %>% mutate(Predicted_outcome = ifelse(abs(difference_in_CS_H) == 0,"D",ifelse(difference_in_CS_H>0,"H",ifelse(difference_in_CS_H<0,"A","NA"))))
```

```{r}
#With the above threshold, get confusion matrix:
attach(pivot_nn_train_combined)
table(Actual_outcome_1,Predicted_outcome)

#if thresholds are: 0 for D, >0 for H, and < 0 for A, then accuracy = 34.7 % [I WONDER HOW MUCH PROFIT WOULD I MAKE FROM THIS SUCCESS RATE, PREDICTING MOSTLY AWAY WINS!]
```
#Trying different thresholds!
```{r}
#creating thresholds for predicted Home winning/A/D

pivot_nn_train_combined <- pivot_nn_train_combined %>% mutate(Predicted_outcome = ifelse(between(difference_in_CS_H,-0.2,0.2),"D",ifelse(difference_in_CS_H>0.2,"H",ifelse(difference_in_CS_H<-0.2,"A","NA"))))
```

```{r}
#With the above threshold, get confusion matrix:
attach(pivot_nn_train_combined)
table(Actual_outcome_1,Predicted_outcome)

#if thresholds are: ifelse(difference_in_CS_H >= -0.2 & difference_in_CS_H <= 0.2,"D",ifelse(difference_in_CS_H>0.2,"H",ifelse(difference_in_CS_H<-0.2,"A","NA")))), then accuracy = 31.7 % [I WONDER HOW MUCH PROFIT WOULD I MAKE FROM THIS SUCCESS RATE, PREDICTING MOSTLY AWAY WINS!]
```

#Trying different thresholds!
```{r}
#creating thresholds for predicted Home winning/A/D

pivot_nn_train_combined <- pivot_nn_train_combined %>% mutate(Predicted_outcome = ifelse(between(difference_in_CS_H,-0.1,0.1),"D",ifelse(difference_in_CS_H>0.1,"H",ifelse(difference_in_CS_H<-0.1,"A","NA"))))
```

```{r}
#With the above threshold, get confusion matrix:
attach(pivot_nn_train_combined)
table(Actual_outcome_1,Predicted_outcome)

#if thresholds are: ifelse(between(difference_in_CS_H,-0.1,0.1),"D",ifelse(difference_in_CS_H>0.1,"H",ifelse(difference_in_CS_H<-0.1,"A","NA")))), then accuracy = 32.4 % [I WONDER HOW MUCH PROFIT WOULD I MAKE FROM THIS SUCCESS RATE, PREDICTING MOSTLY AWAY WINS!]
```
#Trying different thresholds!
```{r}
#creating thresholds for predicted Home winning/A/D

pivot_nn_train_combined <- pivot_nn_train_combined %>% mutate(Predicted_outcome = ifelse(between(difference_in_CS_H,-0.02,0.02),"D",ifelse(difference_in_CS_H>0.02,"H",ifelse(difference_in_CS_H<-0.02,"A","NA"))))
```

```{r}
#With the above threshold, get confusion matrix:
attach(pivot_nn_train_combined)
table(Actual_outcome_1,Predicted_outcome)

#ifelse(between(difference_in_CS_H,-0.02,0.02),"D",ifelse(difference_in_CS_H>0.02,"H",ifelse(difference_in_CS_H<-0.02,"A","NA")))), then accuracy = 32.4 % [I WONDER HOW MUCH PROFIT WOULD I MAKE FROM THIS SUCCESS RATE, PREDICTING MOSTLY AWAY WINS!]
```


#Trying different thresholds!
```{r}
#creating thresholds for predicted Home winning/A/D

pivot_nn_train_combined <- pivot_nn_train_combined %>% mutate(Predicted_outcome = ifelse(between(difference_in_CS_H,-0.5,-0.2),"D",ifelse(difference_in_CS_H>-0.2,"H",ifelse(difference_in_CS_H<-0.5,"A","NA"))))
```

```{r}
#With the above threshold, get confusion matrix:
attach(pivot_nn_train_combined)
table(Actual_outcome_1,Predicted_outcome)

#if thresholds are: ifelse(between(difference_in_CS_H,-0.5,-0.2),"D",ifelse(difference_in_CS_H>-0.2,"H",ifelse(difference_in_CS_H<-0.5,"A","NA")))), then accuracy = 45.3 % [I WONDER HOW MUCH PROFIT WOULD I MAKE FROM THIS SUCCESS RATE, PREDICTING MOSTLY AWAY WINS!]

#You may be overfitting!
```


```{r}
#Now test it for the test data!!! [cuz that is what matters!]
```

