---
title: "Standardization"
author: "Shivam"
date: "April 17, 2019"
output: html_document
---

```{r}
library(dvmisc)
library(caret)
library(readxl)
```

```{r}
library(leaps)
library(pROC)
library(car)
library(mosaic)
library(readxl)
library(readxl)
gw28_onlyndupto <- read_excel("C:/College of Wooster/Sophomore second semester/Math Model/Final Project/Data/gw28 onlyndupto.xlsx")
View(gw28_onlyndupto)
gw15_only_upto_pre16 <- gw28_onlyndupto


```

#Be careful
```{r}
gw28_onlyndupto <- read_excel("C:/College of Wooster/Sophomore second semester/Math Model/Final Project/Data/gw28 onlyndupto.xlsx")
View(gw28_onlyndupto)
gw15_only_upto_pre16 <- gw28_onlyndupto
```


#Converting the Data 
```{r}
gw15_only_upto_pre16$t_assists = gw15_only_upto_pre16$t_assists/ 28
gw15_only_upto_pre16$t_minutes = gw15_only_upto_pre16$t_minutes/ 28
gw15_only_upto_pre16$t_goals_conceded = gw15_only_upto_pre16$t_goals_conceded/ 28
gw15_only_upto_pre16$t_creativity = gw15_only_upto_pre16$t_creativity/ 28
gw15_only_upto_pre16$t_influence = gw15_only_upto_pre16$t_influence/ 28
gw15_only_upto_pre16$threat_t = gw15_only_upto_pre16$threat_t/ 28
gw15_only_upto_pre16$bonus_t = gw15_only_upto_pre16$bonus_t/ 28
gw15_only_upto_pre16$bps_t = gw15_only_upto_pre16$bps_t/ 28
gw15_only_upto_pre16$ict_index_t = gw15_only_upto_pre16$ict_index_t/ 28
gw15_only_upto_pre16$clean_sheets_t = gw15_only_upto_pre16$clean_sheets_t/ 28
gw15_only_upto_pre16$red_cards_t = gw15_only_upto_pre16$red_cards_t/ 28
gw15_only_upto_pre16$yellow_cards_t = gw15_only_upto_pre16$yellow_cards_t/ 28

View(gw15_only_upto_pre16)
```

```{r}
#Now the only data
gw15_only_upto_pre16$assists = gw15_only_upto_pre16$assists-gw15_only_upto_pre16$t_assists
gw15_only_upto_pre16$bonus = gw15_only_upto_pre16$bonus-gw15_only_upto_pre16$bonus_t
gw15_only_upto_pre16$bps = gw15_only_upto_pre16$bps-gw15_only_upto_pre16$bps_t
gw15_only_upto_pre16$clean_sheets = gw15_only_upto_pre16$clean_sheets-gw15_only_upto_pre16$clean_sheets_t
gw15_only_upto_pre16$creativity = gw15_only_upto_pre16$creativity-gw15_only_upto_pre16$t_creativity
gw15_only_upto_pre16$goals_conceded = gw15_only_upto_pre16$goals_conceded-gw15_only_upto_pre16$t_goals_conceded
gw15_only_upto_pre16$goals_scored = gw15_only_upto_pre16$goals_scored-gw15_only_upto_pre16$t_goals_scored
gw15_only_upto_pre16$ict_index = gw15_only_upto_pre16$ict_index-gw15_only_upto_pre16$ict_index_t
gw15_only_upto_pre16$influence = gw15_only_upto_pre16$influence-gw15_only_upto_pre16$t_influence
gw15_only_upto_pre16$minutes = gw15_only_upto_pre16$minutes-gw15_only_upto_pre16$t_minutes
gw15_only_upto_pre16$red_cards = gw15_only_upto_pre16$red_cards-gw15_only_upto_pre16$red_cards_t
gw15_only_upto_pre16$yellow_cards = gw15_only_upto_pre16$yellow_cards-gw15_only_upto_pre16$yellow_cards_t
gw15_only_upto_pre16$threat = gw15_only_upto_pre16$threat-gw15_only_upto_pre16$threat_t
View(gw15_only_upto_pre16)
```

#Writing data
```{r}
write.csv(gw15_only_upto_pre16, file = "gw28_onlynduptoRCorrect.csv")
```
#Combined data train and test
```{r}
library(readxl)
CombinedTraining <- read_excel("C:/College of Wooster/Sophomore second semester/Math Model/Final Project/CombinedTraining.xlsx")

```
#Converting categorical to categorical
```{r}
#CombinedTraining$was_home <- factor(CombinedTraining$was_home)
#CombinedTraining$indreamteam <- factor(CombinedTraining$indreamteam)
View(CombinedTraining)
```

#Dividing data into train and test
```{r}
#Subset into training and testing data
train <- sample(nrow(CombinedTraining), 0.8*nrow(CombinedTraining), replace = FALSE)
P.train <- CombinedTraining[train,]
#P.train<- P #comment this out if you want to do testing
P.test <- CombinedTraining[-train,]
```
#Being careful with the variables for Points and DT
```{r}
P.train_dreamteam<-P.train[c(-63)]
P.train_points<-P.train[c(-64)]
```

#Now training 
```{r}
controlparameters <-trainControl(method="cv", number=5, savePredictions = TRUE, classProbs = TRUE)
parameterGrid <- expand.grid(mtry=c(5,10)) #maybe i could find this no. in matlab?




#creating classification, binary random forest model


modelRandomClass_dt <- train(indreamteam ~ ., data=P.train_dreamteam, method="rf", importance=TRUE, trControl=controlparameters, tuneGrid=parameterGrid)

modelRandomClass_dt
varImp(modelRandomClass_dt)
```
#Now Testing for dreamteam
```{r}
preddreamteamRegress <- predict(modelRandomClass_dt, P.test)
mean((P.test$indreamteam-preddreamteamRegress) ^2)
#Baseline MSE
mean(P.train$indreamteam) #Ask Dr. PAsteur how he got MSE for binary for regression
```
#Now training for points
```{r}
controlparameters <-trainControl(method="cv", number=5, savePredictions = TRUE, classProbs = TRUE)
parameterGrid <- expand.grid(mtry=c(12,17)) #maybe i could find this no. in matlab?




#creating regression for points.


modelRandomClass_1 <- train(F_pts ~ ., data=P.train_points, method="rf", importance=TRUE, trControl=controlparameters, tuneGrid=parameterGrid)

modelRandomClass_1
varImp(modelRandomClass_1)
```
#Now Testing for points
```{r}
preddreamteamRegress <- predict(modelRandomClass_1, P.test)
mean((P.test$F_pts-preddreamteamRegress) ^2)
#Baseline MSE
mean((P.test$points_per_game - P.test$F_pts)^2)
mean((P.train$points_per_game - P.train$F_pts)^2)
```
#Summarywise regression
```{r}
f1 <- as.formula(paste("F_pts~", paste(names(CombinedTraining)[c(42, 57, 51,41,54,58,17,9)], 
                                        collapse="+")))
all<-regsubsets(f1, data = P.train)
#summary(all)
cbind(as.data.frame(summary(all)$which), summary(all)$rsq, summary(all)$adjr2, summary(all)$cp)
```
#fit
```{r}
reg.lm <- lm(F_pts~ t_minutes+ict_index_t+ict_index, data=P.train)
plot(reg.lm)
summary(reg.lm)
vif(reg.lm)
```
#Confidence intervals
```{r}
confint(reg.lm)
```

#Now Testing for points with simple model
```{r}
preddreamteamRegress <- predict(reg.lm, P.test)
View(preddreamteamRegress)
mean((P.test$F_pts-preddreamteamRegress) ^2)
#Baseline MSE
mean((P.test$points_per_game - P.test$F_pts)^2)
#mean((P.train$points_per_game - P.train$F_pts)^2)
```
#Applyin g rtrasnformation
```{r}
F_pts_T<-sqrt(P.train$F_pts)
All_T<-sqrt(P.train$t_minutes+P.train$ict_index_t+P.train$ict_index)
View(All_T)
reg.lm_T <- lm(F_pts_T~ All_T, data =P.train)
plot(reg.lm_T)
summary(reg.lm_T)
#vif(reg.lm_T)
```
#Applying transformation individually
```{r}
mins_T<-sqrt(P.train$t_minutes)
ict_Trans<-sqrt(P.train$ict_index_t)
ict_Trans_notavg<-sqrt(P.train$ict_index)

#View(F_pts_T)
reg.lm_T_two <- lm(F_pts_T~ mins_T+ict_Trans+ict_Trans_notavg, data=P.train)
plot(reg.lm_T_two)
summary(reg.lm_T_two)
vif(reg.lm_T_two)
```
#Now Testing MSE for the two new regression models.
```{r}
preddreamteamRegress_2 <- predict(reg.lm_T, P.test)
View(preddreamteamRegress_2)
mean((P.test$F_pts-preddreamteamRegress_2) ^2)

preddreamteamRegress_3 <- predict(reg.lm_T_two, P.test)
mean((P.test$F_pts-preddreamteamRegress_3) ^2)
```
#Predicting gw 35 using gw34
```{r}
library(readxl)
gw34_onlynduptoRCorrect <- read_excel("C:/College of Wooster/Sophomore second semester/Math Model/Final Project/gw34_onlynduptoRCorrect.xlsx")
```

```{r}
predF_pts_rf <- predict(modelRandomClass_1, gw34_onlynduptoRCorrect)
predd_team_rf <- predict(modelRandomClass_dt, gw34_onlynduptoRCorrect)
gw34_onlynduptoRCorrect<-cbind(gw34_onlynduptoRCorrect[,1], predF_pts_rf, predd_team_rf)
write.csv(gw34_onlynduptoRCorrect,"PredictionForm.csv")
```

```{r}
cor(P.train$completed_passes, P.train$F_pts)
cor(P.train$threat_t, P.train$F_pts)
cor(P.train$bps_t, P.train$F_pts)
cor(P.train$clean_sheets, P.train$F_pts)
cor(P.train$clean_sheets_t, P.train$F_pts)
cor(P.train$bonus_t, P.train$F_pts)
cor(P.train$transfers_balance, P.train$F_pts)
cor(P.train$transfers_out, P.train$F_pts)
cor(P.train$selected_by_percent, P.train$F_pts)
```

